A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-05 Paper.tex

\section{Beacon Initialization}
Beacons initialization refers to the precursor process to the EKF where beacons (or landmarks) whose initial positions are not known are estimated. One of the complications with RO-SLAM involves the issue of the EKF, which is used by many implementations, being  sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These methods are further  divided into delayed and undelayed initializations.
\subsection{Delayed/Offline initializations}
These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman2003},a posed based ekf as mentioned in \cite{} , a moving horizon estimation as mentioned in [9] etc. The most popular ones are mentioned below.

@@

\end{figure}
\subsubsection{Trilateration}
[Pure Porbablisitc approach to RO  SLAM] mentions a basic trilateration technique involving geometric intersection. Rings are drawn at different points of the robots path as shown in Fig[a] , where the radius of the rings depend on the strength of the received signals from the beacons. This method of initialization is highly ambiguous as the rings can have more than 1 point of intersecting as shown in Fig[b]  or no  intersecting points as shown in Fig[c]. %more paperes needed
\subsubsection{Particle filter}
This takes a more probabilistic approach to estimating the initial location of the beacons. As mentioned in[thrun particle filter paper] initially the entire space is represented by particles. These particles are resampled based on importance weights every iteration. There are several resampling methods mentioned in[methods paper]. Eventually the particle set converges to the accurate location of the beacons. Though this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.

@@

Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented. An IF algorithm is mentioned in[ probobilistic robotics book]. In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix. This makes the SEIF more scalable and effiecient as show in [SEIF paper1]

@@

In [SEIF PAER 1] they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process. Hence the computer burden on the robot is reduced. In addition they factored in inter beacon measurements to reduce uncertainity even furthur. In \cite{Djugash2006} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.

@@

\subsection{Graph SLAM}
Graph SLAM unlike the EKF solves the full SLAM problem. It is similar to the information filter in the way it represents the Gaussian  in the form of its information filter and information matrix. The key difference is in the sparseness maintained in the information matrix due to linearizion in graph SLAM as mentioned in[Probablisitic robotics]. This allows for the use of variable elimination algorithms and also maintain higher dimensional maps which were not possible using EKF.

@@

\subsection{Particle}      %change the references
Particles filters are made ue up various monte carlo algorithms. they are used to estimate states in partially observable Markov chains as shown in [9]. In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14] which EKF in comparison has it drawbacks. It has also been at the core higher dimensional computational problems.  
%Description
Initially robot assumes global uncertainity through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities[sampling methods paper]. After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
\begin{figure}[h!]
	\centering
	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the robot location. }

@@

As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment. 
EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information[probablistic robotics]
As the number of particles increases the computational complexity of the filter too increases. In order to address this there were several new methods introduced that  exploit the independence among state variables. For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from [Fast slam paper]. It also solves the data association problem previously unsolved by EKF[8].

@@

	FastSLAM utilizes the conditional Independence property of SLAM applications. If the path of the robot is known the correlation between the landmarks becomes zero. Hence in FastSLAM the robot path is initialised by using a particle fitler. Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in [Fast Slam paper 1]. Thus it maintains mutliple data hypothesis overcoming the EKF problem.

	As mentioned in [probablisitic robotics] the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficency. In order to overcome this Rao blackwe the algorithm was tweaked to have a better target distrubtion in FASTSLAM 2.0. It was called the Rao-Blackwellized particle filter as mentioned in[fast slam 2]

>>>>

\section{Beacon Initialization}
Beacons initialization refers to the precursor process to the EKF where beacons (or landmarks) whose initial positions are not known are estimated. One of the complications with RO-SLAM involves the issue of the EKF, which is used by many implementations, being  sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These methods are further  divided into delayed and undelayed initializations.
\subsection{Delayed/Offline initializations}
These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{} , a moving horizon estimation as mentioned in [9] etc. The most popular ones are mentioned below.

@@

\end{figure}
\subsubsection{Trilateration}
\cite{Thrun2002} mentions a basic trilateration technique involving geometric intersection. Rings are drawn at different points of the robots path as shown in Fig[a] , where the radius of the rings depend on the strength of the received signals from the beacons. This method of initialization is highly ambiguous as the rings can have more than 1 point of intersecting as shown in Fig[b]  or no  intersecting points as shown in Fig[c]. %more paperes needed
\subsubsection{Particle filter}
This takes a more probabilistic approach to estimating the initial location of the beacons. As mentioned in\cite{Thrun2002a} initially the entire space is represented by particles. These particles are resampled based on importance weights every iteration. There are several resampling methods mentioned in \cite{Li2015}. Eventually the particle set converges to the accurate location of the beacons. Though this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.

@@

Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented. An IF algorithm is mentioned in\cite{Torres-Gonzalez2014}. In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix. This makes the SEIF more scalable and effiecient as show in\cite{Torres-Gonzalez2014}

@@

In \cite{Torres-Gonzalez2014} they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process. Hence the computer burden on the robot is reduced. In addition they factored in inter beacon measurements to reduce uncertainity even furthur. In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.

@@

\subsection{Graph SLAM}
Graph SLAM unlike the EKF solves the full SLAM problem. It is similar to the information filter in the way it represents the Gaussian  in the form of its information filter and information matrix. The key difference is in the sparseness maintained in the information matrix due to linearizion in graph SLAM as mentioned in\cite{Thrun2002a}. This allows for the use of variable elimination algorithms and also maintain higher dimensional maps which were not possible using EKF.

@@

\subsection{Particle}      %change the references
Particles filters are made ue up various monte carlo algorithms. they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}. In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem\cite{Engelson1992} which EKF in comparison has it drawbacks. It has also been at the core higher dimensional computational problems.  
%Description
Initially robot assumes global uncertainity through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
\begin{figure}[h!]
	\centering
	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the robot location. }

@@

As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment. 
EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}
As the number of particles increases the computational complexity of the filter too increases. In order to address this there were several new methods introduced that  exploit the independence among state variables. For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from [Fast slam paper]. It also solves the data association problem previously unsolved by EKF[need to add paper].

@@

	FastSLAM utilizes the conditional Independence property of SLAM applications. If the path of the robot is known the correlation between the landmarks becomes zero. Hence in FastSLAM the robot path is initialised by using a particle fitler. Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{}. Thus it maintains mutliple data hypothesis overcoming the EKF problem.

	As mentioned in \cite{Thrun2002a} the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficency. In order to overcome this Rao blackwe the algorithm was tweaked to have a better target distrubtion in FASTSLAM 2.0. It was called the Rao-Blackwellized particle filter as mentioned in \cite{Montemerlo2003}
